---
title: "Using the SRA2R Package"
output: 
  BiocStyle::html_document
date: "`r doc_date()`"
package: "`r pkg_ver('SRA2R')`"
abstract: >
  The SRA2R package is a high-performance interface to SRA data from within R.  
vignette: >
  %\VignetteIndexEntry{Using the SRA2R Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

# Introduction
Developed in 2007 with the object of storage data from large scale 
studies including the Human Micorbiome Project as well the 1000 
GenomesProject, the Sequencing Read Archive (SRA) is a public 
repository developed as an initiative from the National Center for 
Biotechnology Information (NCBI), the European Bioinformatics 
Institute (EBI), and the DNA Data Bank of Japan (DDBJ).

Developed in 2007 to allocate raw sequencing data from biological 
studies, processed by different platforms as Roche-454 Life Sciences, 
Illumina Solexa and Applied Biosystems SOLiD.



# Usage


## SRA Overview and Introspection Functions

The following dependencies are necessary for using this package: 
*Biostrings*, *XVector*, *IRanges*, *S4Vectors*.

### Stats

The *readCount2* function contains information of run acession 
number, and count the total number reads and reads after alingnment.
```{r}
library(SRA2R)
readCount2('SRR2971307')
```

*getReference* makes possible get access to all chomosome references 
and extract information as the canonical and common names, length and
alignment counts for each. 
```{r}
getReference('SRR2971307')
```

To have access to a complete nucleotide sequence for each reference, 
the function *refBases* will return a list with the full sequence.
(NOT SURE IF THIS ONE SHOULD BE HERE OR NOT, IN STATS)
```{r}
refBases('SRR2971307')
```

## Getting Reads 

To get access to the reads in a read collection, you can use any of 
the following functions:
*getFastqCount* simply returns the full read count;
*getFastqReads* returns a list with the entire sequence of all reads;
*getFastqReadsWithQuality* returns a list with the quality 
information for the entire sequence of all reads
```{r}
getFastqCount('SRR2971307')
```

```{r}
getFastqReads('SRR2971307',10)
```

```{r}
getFastqReadsWithQuality('SRR2971307',10)
```

